Community-Conditioned Language Models

### 2020-11-02 paper/paper.tex
possible intro structure

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{pgfplots}
\usepackage{todonotes}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepgfplotslibrary{groupplots}
\pgfplotsset{compat=1.16}

@@

@@

@@

\begin{enumerate}
\item Different communities have different levels of linguistic
  complexity
\item different language models are able to recognize such differences
\item level at which the community embedding is taken into account in the language model influences this.
\item community vectors are correlated with extra-linguistic information.
\item stability is correlated with language complexity
\end{enumerate}

@@

- computer r2.

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2020}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{pgfplots}
\usepackage{todonotes}
\usepackage{enumitem}
\renewcommand{\UrlFont}{\ttfamily\small}
\usepgfplotslibrary{groupplots}
\pgfplotsset{compat=1.16}

@@

\newlist{hypotheses}{enumerate}{3}
\setlist[hypotheses,1]{parsep=0pt,itemsep=1pt,font=\bfseries,label=(H\arabic*)}

@@

- What are linguistic communities
  - Linguistic complexity
- Conditioned language models

@@

\begin{hypotheses}
\item Different communities have different levels of linguistic
  complexity
\item Different language models are able to recognize such differences
\item The level at which the community embedding is taken into account
  in the language model influences this.
\item Community embedding are correlated with extra-linguistic
  properties of the community.
\item Community stability is correlated with language complexity
\end{hypotheses}

@@

- compute pearson correlation coefficient
